### 2017-11-15 Risk analysis/Text/Layout/Layout/chapter3_results.tex
Including Figures

		\section{Results using the 3D geological model}

		- results of ML1 generally similar as for ML3:
			i.e. thicker reservoir does not mean higher volume, as we didn't implement a direct uncertainty to the shape, the spill point will stay more or less the same
			-> spill and leak point as limiting factors to max volume
			-> max volume already defined in prior (ROV max 5,500,000)
		- see ML2: seal thickness as decisive factor
			-> if seal thin and reservoir thick see the ratio of both!), higher likelihood of surpassing SSF

>>>>

		\section{3D geological model results}
		- first: MC simulation of only prior uncertainty error propagation to generate a prior reference model
		- second: Bayesian inference using only thickness likelihoods
		- third: Bayesian inference including SSF likelihood
		- last test: BI using only SSF likelihood

		\subsection{Prior model}
		\begin{figure}[h]
			\centering
			\includegraphics[width=1\textwidth]{Figures/M_prior}
			\caption{....}\label{fig:M_prior}
		\end{figure}

		\subsection{Posterior model I}
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML1}
			\caption{....}\label{fig:ML1}
		\end{figure}

		\subsection{Posterior model II}%ML3
		-results similar to I, basically same
		- results of ML1 generally similar as for ML3:
		i.e. thicker reservoir does not mean higher volume, as we didn't implement a direct uncertainty to the shape, the spill point will stay more or less the same
		-> spill and leak point as limiting factors to max volume
		-> max volume already defined in prior (ROV max 5,500,000)

		\subsection{Posterior model III}%ML2
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML2}
			\caption{....}\label{fig:ML2}
		\end{figure}
		- see ML2: seal thickness as decisive factor
			-> if seal thin and reservoir thick see the ratio of both!), higher likelihood of surpassing SSF
